Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-06-26 WSSSPE2_report/WSSSPE2_review.tex
Secion 6: Added line breaks. Commented out two notes.

\item \textbf{Alice Allen: Find it! Cite it! }%~\cite{Allen_poster}}
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change.
\begin{comment}
The ASCL actively looks for opportunities to use change management strategies to
move astronomy to a more transparent discipline; these strategies can be used in
other disciplines to further change in them.
\end{comment}
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exploring Sustainability} \label{sec:exploring}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{Colin led writing of this section.}

\note{\href{http://tinyurl.com/mpbhvyb}{Google doc notes}}
%https://docs.google.com/a/uchicago.edu/document/d/10XkshP3YjXnA5JQgP-UFHbOxshWczzehWGSo6V7bNH4/edit

>>>>

\item \textbf{Alice Allen: Find it! Cite it! }%~\cite{Allen_poster}}
The Astrophysics Source Code Library (ASCL) is an online registry of
scientist-written software used in astronomy research. Their primary interest is
rendering research more transparent by making this software more discoverable for
examination. The ASCL is treated as a publication by an indexing resource for
astronomy, the Astrophysics Data System (ADS). ADS tracks citations to what it
indexes, including citations to ASCL entries. Increasing rewards for writing
software, whether through citation, transitive credit or other methods, gives
software authors a powerful reason to take the time to build sustainability into
their software and is an excellent way to drive community change.
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Exploring Sustainability} \label{sec:exploring}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Colin led writing of this section.}

%\note{\href{http://tinyurl.com/mpbhvyb}{Google doc notes}}
%https://docs.google.com/a/uchicago.edu/document/d/10XkshP3YjXnA5JQgP-UFHbOxshWczzehWGSo6V7bNH4/edit
